Supporting Information for\\ ``Local fitness and epistatic effects lead to distinct patterns of linkage disequilibrium in protein-coding genes''

### 2022-04-01 manuscript/paper.tex
ok now i'm ready

\title{A heterogeneous landscape of selection and epistasis in protein-coding genes revealed by two-locus statistics}
\author[]{Aaron P. Ragsdale}
\affil[]{Department of Integrative Biology, University of Wisconsin, Madison, WI, USA}
\affil[]{apragsdale@wisc.edu}
\maketitle

>>>>

%\title{A heterogeneous landscape of selection and epistasis in protein-coding genes revealed by two-locus statistics}
\title{Local fitness and epistatic effects lead to distinct patterns of linkage disequilibrium in protein-coding genes}
\author[]{Aaron P. Ragsdale}
\affil[]{Department of Integrative Biology, University of Wisconsin--Madison, WI, USA}
\affil[]{apragsdale@wisc.edu}
\maketitle

### 2022-04-01 manuscript/supplement.tex
ok now i'm ready

\title{Supporting Information for\\
``A heterogeneous landscape of selection and epistasis in protein-coding genes revealed by two-locus statistics''}
\author[]{Aaron P. Ragsdale}
\affil[]{Department of Integrative Biology, University of Wisconsin, Madison, WI, USA}
\affil[]{apragsdale@wisc.edu}
\date{\today}
\maketitle

>>>>

\title{Supporting Information for\\
``Local fitness and epistatic effects lead to distinct patterns of linkage disequilibrium in protein-coding genes''}
\author[]{Aaron P. Ragsdale}
\affil[]{Department of Integrative Biology, University of Wisconsin--Madison, WI, USA}
\affil[]{apragsdale@wisc.edu}
\date{\today}
\maketitle
